Arhangelskii's \(\alpha\)-principles and selection games

### 2020-10-29 articles/selection-alpha-games/article.tex
add notes from Carolinas topology seminar
incorporate referee feedback

Such games are well-represented in the literature; see \cite{MR1378387}
for example.
We will also consider the similarly-defined games \(G_{<2}(\mc A,\mc B)\)
(\(\plII\) chooses 0 or 1 points from each choice by \(\plI\)) and \(G_{cf}(\mc A,\mc B)\)
(\(\plII\) chooses cofinitely-many points).

@@

We briefly note that the statement \(\plI\notprewin G_\star(\mc A,\mc B)\)
is often denoted as the \term{selection principle} \(S_\star(\mc A,\mc B)\).

@@

Now suppose \(\plI\notprewin G_1(\mc A,\mc B)\). Given \(A_n\in\mc A\) for \(n<\omega\),
first choose \(A_n'\in\mc A\) such that \(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\),
\(j<k\) implies \(a_{n,j}\not=a_{n,k}\),
and \(A_{n,m}=\{a_{n,j}:m\leq j<\omega\}\in\mc A\).
Finally choose
some \(\theta:\omega\to\omega\) such that \(|\theta^{\leftarrow}(n)|=\aleph_0\) for
each \(n<\omega\).

@@

\begin{corollary}
Let \(\mc B\) be \(\Gamma\)-like and \(\mc B\subseteq\mc A\).
Then 
\begin{itemize}
\item \(\plI\notwin G_{fin}(\mc A,\mc B)\) if and only if
\(S_{fin}(\mc A,\mc B)\) if and only if
\(\alpha_2(\mc A,\mc B)\), and
\item \(\plI\notwin G_{1}(\mc A,\mc B)\) if and only if
\(S_{1}(\mc A,\mc B)\) if and only if
\(\alpha_4(\mc A,\mc B)\).
\end{itemize}
\end{corollary}

@@

We take advantage of the following lemma.

>>>>

Such games are well-represented in the literature; see \cite{MR1378387}
for example.
We will also consider the similarly-defined games \(G_{<2}(\mc A,\mc B)\)
(\(\plII\) chooses 0 or 1 points from each choice by \(\plI\)) and \(G_{cf}(\mc A,\mc B)\)
(\(\plII\) chooses cofinitely-many points). We use \(G_\star(\mc A,\mc B)\)
to denote an arbitrary selection game.

@@

We briefly note that the statement \(\plI\notprewin G_\star(\mc A,\mc B)\)
is more often denoted as the \term{selection principle}
\(S_\star(\mc A,\mc B)\). However, we will generally characterize
results in terms of selection games rather than selection principles
in order to emphasize the commonalities between the statements
\(\plI\notwin G_\star(\mc A,\mc B)\) and
\(\plI\notprewin G_\star(\mc A,\mc B)\).

@@

Now suppose \(\plI\notprewin G_1(\mc A,\mc B)\). Given \(A_n\in\mc A\) for \(n<\omega\),
first choose \(A_n'\in\mc A\) such that \(A_n'=\{a_{n,j}:j<\omega\}\subseteq A_n\),
\(j<k\) implies \(a_{n,j}\not=a_{n,k}\),
and \(A_{n,m}=\{a_{n,j}:m\leq j<\omega\}\in\mc A\).
Finally choose
some \(\theta:\omega\to\omega\) such that \(|\theta^{\leftarrow}(n)|=\aleph_0\) for
each \(n<\omega\)
(where \(\theta^{\leftarrow}\) denotes the inverse set map.

@@

\begin{corollary}
Let \(\mc B\) be \(\Gamma\)-like and \(\mc B\subseteq\mc A\).
Then 
\begin{itemize}
\item \(\plI\notwin G_{1}(\mc A,\mc B)\) if and only if
\(S_{1}(\mc A,\mc B)\) if and only if
\(\alpha_2(\mc A,\mc B)\).
\item \(\plI\notwin G_{fin}(\mc A,\mc B)\) if and only if
\(S_{fin}(\mc A,\mc B)\) if and only if
\(\alpha_4(\mc A,\mc B)\), and
\end{itemize}
\end{corollary}

@@

We take advantage of the following lemma. The citation is given to Peter Nyikos who provides
a nice proof. At a 2020 Fall meeting of the Carolinas Topology Seminar,
it was suggested by Alan Dow that this lemma may be known as the
``[Hausdorff] Disjoint Refinement Lemma'', as found in e.g. \cite[Lemma 3.4]{COMFORT1996149}.
